What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-25 android-stacks.tex
best practices

\subsection{Exceptions in Java} \label{sec:extypes}

@@

\subsection{Related Best Practices}
\label{sec:best}

Several general guidelines have been proposed on how to use Java
exceptions~\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,
bloch2008effective}. 
We compiled a list of the guidelines related to exception types and exception propagation in Java, summarized below:\footnote{We also compiled guidelines related
to exception handling but they are out of the scope of this paper.}

@@

  \item[RQ2] What patterns of exception (mis)-use related to exception types and exception propagation emerge from the exception stack trace analysis?

>>>>

\subsection{Exception Types in Java} \label{sec:extypes}

@@

\subsection{Best Practices}
\label{sec:best}

There is a long-lasting debate about the pros and cons of checked and unchecked exceptions 
~\cite{javatut,stackoverlow,debate},\footnote{152 questions in Stackoverlow
are related to this debate}. Such debates, however, are mainly based on the developers own experience in
using both types - since there is of a lack empirical studies on their the pros and cons.

Nevertheless, several general guidelines have been proposed on how to use Java
exceptions~\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,
bloch2008effective}, regardless the exception type chosen. Such guidelines do not focus on 
advocating any specific type but rather propose ways to effectively use each of them.
 We compiled a list of the guidelines related to exception types in Java, 
summarized below:\footnote{We also compiled guidelines related
to exception handling but they are out of the scope of this paper.}

@@

  \item[RQ2] \noindent\emph{What patterns of exception (mis)-use related to exception types and propagation emerge from the exception stack trace analysis?}
